---
output:
  github_document
---

AppEEARS4R
========

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.path='inst/img/'
)
```


`AppEEARS4R` is an R client for interacting with the LP DAAC's Application for Extracting and Exploring Analysis Ready Samples [(AρρEEARS)](https://lpdaac.usgs.gov/tools/appeears/) interface. AppEEARS allows for users to easily subset DAAC datasets spacially and temporally. This package provides a progammatic interface for submitting requests to and receiving data from AppEEARS.


Available data sets can be explored on the [LP DAAC website](https://lpdaac.usgs.gov/product_search/). Accessing data requires an [Eartdata Login account](https://urs.earthdata.nasa.gov/users/new?_ga=2.146602164.1614539679.1607373041-824518196.1579722432/).


## Installation

This package is not currently available on CRAN and must be installed from source.

```{r eval=FALSE}
install.packages("devtools")
library('devtools')
devtools::install_github("usa-npn/AppEEARS4R")
```

```{r}
library('AppEEARS4R')
```



## The Basics

This package includes a series of functions for interacting with AppEEARS at each step of establishing a session, making a request, and downloading the results. There's also a coordinating function that ties all the subodrindate functions together. The most appropriate way to use the package depends on the size of your requests and your use case. Below is an example of using the coordinating function.

```{r eval=FALSE}
point_df <-data.frame(lat=c(42.3),long=c(-86.4),id=c(1),category=c("Test"))
appeears_get_data(your_user_name,your_pass_word,"MyTest","2014-01-01","2014-01-31","MCD12Q2.006",c("Greenup"),type="point",point_df,base_path="./data/")
```

This will download the "Greenup" layer data for the given point from the MCD12Q2.006 product into the "data" folder.



## Acknowledgements

This code was developed, in part, as part of the integrated [Pheno-Synthesis Software Suite (PS3)](https://git.earthdata.nasa.gov/projects/APIS/repos/pheno-synthesis-software-suite/browse).  The authors acknowledge funding for this work through NASA's AIST program  (80NSSC17K0582, 80NSSC17K0435, 80NSSC17K0538, and 80GSFC18T0003). The University of Arizona and the USA National Phenology Network's efforts with this package are supported in part by US Geological Survey (G14AC00405, G18AC00135) and the US Fish and Wildlife Service (F16AC01075 and F19AC00168).  The development of PhenoCam was supported by the Northeastern States Research Cooperative, the NSF Macrosystems Biology program (EF-1065029 and EF-1702697), the Department of Energy Regional and Global Climate Modeling program (DE-SC0016011), the US National Park Service Inventory and Monitoring Program and the US Geological Survey (G10AP00129, G16AC00224).
